Extrinsic Calibration of 2D Laser Range Finders \\ using Planar Features

### 2019-03-30 paper.tex
final adjustements, like authors filliations

\author{\IEEEauthorblockN{Bernardo Lourenço}
\IEEEauthorblockA{\textit{Departamento de Engenharia Mecânica} \\
\textit{Universidade de Aveiro}\\
Aveiro, Portugal \\
bernardo.lourenco@ua.pt}
\and
\IEEEauthorblockN{Paulo Dias}
\IEEEauthorblockA{\textit{IEETA} \\
\textit{Universidade de Aveiro}\\
Aveiro, Portugal \\
paulo.dias@ua.pt}
\and
\IEEEauthorblockN{Miguel Riem Oliveira}
\IEEEauthorblockA{\textit{Departamento de Engenharia Mecânica} \\
\textit{Universidade de Aveiro}\\
Aveiro, Portugal \\
mriem@ua.pt}
}

@@

\IEEEpubidadjcol

@@

The 2D-LRF is a sensor that outputs several laser scans. Each laser scan is a set of range measurements taken sequentially along several directions all coincident with a plane: the scanning plane. That is in fact why this equipment has a 2D nature. Thus, for each scan, a 2D slice of the scene is measured. Since the LRF is mounted on top of an actuated kinematic chain (the PTU), the movement of this chain positions the LRF in different poses in the 3D space. Through the accumulation of the several laser scans, a dense point cloud of the scene is produced. It is important to consider that the scan is not acquired instantaneously. However, if the speed of the LRF is low, its effects are negligible.

>>>>

\DeclareRobustCommand*{\IEEEauthorrefmark}[1]{%
  \raisebox{0pt}[0pt][0pt]{\textsuperscript{\footnotesize #1}}%
}

\author{
    \IEEEauthorblockN{
        Bernardo Lourenço\IEEEauthorrefmark{1},
        Paulo Oliveira\IEEEauthorrefmark{2,3}
        and Miguel Oliveira\IEEEauthorrefmark{1,3,4,5}}
    \IEEEauthorblockA{\IEEEauthorrefmark{1}Departamento de Engenharia Mecânica, Universidade de Aveiro, Portugal}
    \IEEEauthorblockA{\IEEEauthorrefmark{2}Departamento de Electrónica, Telecomunicações e Informática, Universidade de Aveiro, Portugal}
    \IEEEauthorblockA{\IEEEauthorrefmark{3}Institute of Electronics and Informatics Engineering of Aveiro, Universidade de Aveiro, Portugal}
    \IEEEauthorblockA{\IEEEauthorrefmark{4}Centro de Tecnologia Mecânica e Automação (TEMA), Universidade de Aveiro, Portugal}
    \IEEEauthorblockA{\IEEEauthorrefmark{5}Instituto de Engenharia de Sistemas e Computadores, Tecnologia e Ciência, Portugal}}

@@

@@

The 2D-LRF is a sensor that outputs several laser scans. Each laser scan is a set of range measurements taken sequentially along several directions, all coincident with a plane: the scanning plane. That is in fact why this equipment has a 2D nature. Thus, for each scan, a 2D slice of the scene is measured. Since the LRF is mounted on top of an actuated kinematic chain (the PTU), the movement of this chain positions the LRF in different poses in the 3D space. Through the accumulation of the several laser scans, a dense point cloud of the scene is produced. Note that, theoretically, the movement of the PTU may influence the measurements of the single scan. However, because the frequency of scanning acquisition is high, and the velocity of the joints of the PTU is low, this effect was not considered in this work.
